\pkg{webchem}: An \proglang{R} Package to Retrieve Chemical Information from the Web

### 2020-04-01 revision3_2581/paper.tex
Updated corresponding author affiliation

\author{
	Eduard Sz\"ocs\\Universit\"at Koblenz-Landau \And
	Tam\'as Stirling\\Independent Developer \And
	Eric Scott\\Tufts University \And
	Andreas Scharm\"uller\\Universit\"at Koblenz-Landau \And
    Ralf B. Sch\"afer\\Universit\"at Koblenz-Landau}
\title{\pkg{webchem}: An \proglang{R} Package to Retrieve Chemical Information from the Web}

@@

\Address{
  Eduard Sz\"ocs\\
  Institute for Environmental Sciences\\
  Universit\"at Koblenz-Landau\\
  Fortstra{\ss}e 7\\
  76829 Landau, Germany\\
  E-mail: \email{szoecs@uni-landau.de}\\
  URL: \url{https://edild.github.io}\\
  \\
  Tam\'as Stirling\\
  Budapest, Hungary\\
  E-mail: \email{stirling.tamas@gmail.com}\\
  URL: \url{https://github.com/stitam}
}

>>>>

\author{
	Eduard Sz\"ocs\\Universit\"at Koblenz-Landau \And
	Tam\'as Stirling\\Independent Researcher \And
	Eric Scott\\Tufts University \AND
	Andreas Scharm\"uller\\Universit\"at Koblenz-Landau \And
    Ralf B. Sch\"afer\\Universit\"at Koblenz-Landau}
\title{\pkg{webchem}: An \proglang{R} Package to Retrieve Chemical Information from the Web}

@@

\Address{
  Tam\'as Stirling\\
  Independent Researcher \\
  Budapest, Hungary\\
  E-mail: \email{stirling.tamas@gmail.com}\\
  URL: \url{https://github.com/stitam}
}
